\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-04 cubble.Rmd
Update section 4.5

Interactive graphics can be especially useful for spatio-temporal data because they make it possible to look at the data in multiple ways on-the-fly. The last example describes the process of using cubble with the \pkg{crosstalk} package to build an interactive display connecting a map of Australia, with ribbon plots of temperature range observed at the stations in 2020. The purpose is to explore the variation of monthly temperature range over the country.

We will first summarise the daily data in \code{climate_aus} into monthly average and calculate the variance of the temperature difference, which will be used to color the temperature band later.

>>>>

Interactive graphics can be especially useful for spatio-temporal data because they make it possible to look at the data in multiple ways on-the-fly. This last example describes the process of using 
\pkg{cubble} with the \pkg{crosstalk} package to build an interactive display connecting a map of Australia, with ribbon plots of temperature range observed at a group of stations in 2020. The purpose is to explore the variation of monthly temperature range over the country.

Firstly, we summarise the daily data in \code{climate_aus} into monthly averages and calculate the variance of the monthly averages differences between the minimum and maximum temperatures. This variance will be used to color the temperature band later.
